Stack Safety is a Security Property

### 2021-04-10 tex/main.tex
Couple more things

In summary, we offer the following contributions:
\begin{itemize}
\item
  We adapt formulations of integrity and confidentiality from
  language-based security
  to formalize a parameterized {\em stepwise stack-safety property} and argue that
  it captures the intuitive concepts of local stack encapsulation, well-bracketed control
  flow, and temporal stack safety~(\cref{sec:lse-and-wbcf}).
\item
  We apply a property-based randomized testing framework to provide evidence that
  this stepwise property is enforced by the Depth Isolation policy
  of~\citet{DBLP:conf/sp/RoesslerD18}~(\cref{sec:conservative}).
\item
  We formalize a weaker but more extensional \emph{observational} variant of the
  stack safety property and argue that it accurately characterizes
  the Lazy Tagging and Clearing policy of~\citet{DBLP:conf/sp/RoesslerD18}
  enhanced with unique tags on each activation~(\cref{sec:lazy}).
\item
  We show how our models can be instantiated and extended to handle passing
  arguments on the stack~(\cref{sec:??}) and simple
  coroutines~(\cref{sec:??}).
%  This policy does not enforce our strict
%  local state encapsulation property,
%  but a modified version of it using unique per-activation tags enforces
%  an (also provably) weaker lazy variant of the property, which still prohibits
%  the same intuitively stack unsafe behaviors.
%
% \apt{Awkward, but the truth I fear.} \bcp{I agree the phrasing is awkward,
%   but the point we can make is still strong: To make the property easier
%   to enforce, we can slightly weaken its guarantees; the weaker version is
%   a bit more complicated to state but still retains the pragmatic
%%   protections of the original.}\apt{To clarify: Nick's LT\&C policy uses
%   depth-based tags, which do not enforce even our lazy policy. So we need to
%   introduce a version of LT\&C that uses unique activation tags.}

  %\item As evidence that the property is not too strong\apt{But we add the lazy version because the strict version \emph{is} too strong, in some sense.}, we show that it is
%  realizible by
%  a previously proposed micro-policy enforcement
%  mechanism~(\Cref{sec:micro-policy}). \leo{And it says yes on a
%    substantial body of code}. We also present a variation of the
%  property + policy that is lazy, easier/more efficient to implement,
%  and provably weaker (\Cref{sec:lazy}).
%\item A provably stronger (inductive? step-by-step/stepwise) variant
%  of this property tuned for testing/verification.  We test the whole
%  thing with a cool framework. \bcp{Which section?}
\end{itemize}
\Cref{sec:relwork} discusses related work;
\cref{sec:future} sketches directions for future work.

>>>>

In summary, we offer the following contributions: \bcp{Section numbers are
  wonky---why just 7.1, where is 8, etc.}
\begin{itemize}
\item
  We adapt formulations of integrity and confidentiality from
  language-based security
  to formalize a parameterized {\em stepwise stack-safety property} and argue that
  it captures the intuitive concepts of local stack encapsulation, well-bracketed control
  flow, and temporal stack safety~(\cref{sec:lse-and-wbcf}).
\item
  We use a property-based randomized testing framework to support the claim
  that this stepwise property is actually enforced by the Depth Isolation policy
  of~\citet{DBLP:conf/sp/RoesslerD18}~(\cref{sec:conservative}).
\item
  We formalize a weaker but more extensional \emph{observational} variant of the
  stack safety property and argue that it accurately characterizes
  the Lazy Tagging and Clearing policy of~\citet{DBLP:conf/sp/RoesslerD18}
  enhanced with unique tags on each activation~(\cref{sec:lazy}).
\item
  We show how our models can be instantiated and extended to handle passing
  arguments on the stack~(\cref{sec:??}) and simple
  coroutines~(\cref{sec:??}).\bcp{``instantiated and extended'' is awkward.
  Maybe ``We show how our models can be instantiated to handle passing
  arguments on the stack~(\cref{sec:??}) and extended with simple
  coroutines~(\cref{sec:??}).''  If that's what we mean.}
%  This policy does not enforce our strict
%  local state encapsulation property,
%  but a modified version of it using unique per-activation tags enforces
%  an (also provably) weaker lazy variant of the property, which still prohibits
%  the same intuitively stack unsafe behaviors.
%
% \apt{Awkward, but the truth I fear.} \bcp{I agree the phrasing is awkward,
%   but the point we can make is still strong: To make the property easier
%   to enforce, we can slightly weaken its guarantees; the weaker version is
%   a bit more complicated to state but still retains the pragmatic
%%   protections of the original.}\apt{To clarify: Nick's LT\&C policy uses
%   depth-based tags, which do not enforce even our lazy policy. So we need to
%   introduce a version of LT\&C that uses unique activation tags.}

  %\item As evidence that the property is not too strong\apt{But we add the lazy version because the strict version \emph{is} too strong, in some sense.}, we show that it is
%  realizible by
%  a previously proposed micro-policy enforcement
%  mechanism~(\Cref{sec:micro-policy}). \leo{And it says yes on a
%    substantial body of code}. We also present a variation of the
%  property + policy that is lazy, easier/more efficient to implement,
%  and provably weaker (\Cref{sec:lazy}).
%\item A provably stronger (inductive? step-by-step/stepwise) variant
%  of this property tuned for testing/verification.  We test the whole
%  thing with a cool framework. \bcp{Which section?}
\end{itemize}
\Cref{sec:relwork} discusses related work, and 
\cref{sec:future} sketches directions for future work.
